### 2022-11-15 NSF2022/Description/summary.tex
...

\vspace{-0.1in}
\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates variational techniques and offers
insight into fundamentals of self-organization and collective dynamics.
The project brings socially consequential research into the classroom
and offers undergraduates the opportunity to train alongside faculty and
graduate students. With its unique combination of mathematical modeling,
analysis, and scientific computing, the project highlights the potential
advancement of STEM from Applied Mathematics.

>>>>

\vspace{-0.1in}
\subsection*{Broader Impacts}
\vspace{-0.1in}
This project aims to advance the mathematical modeling of collective
dynamics of amphiphilic granules. The framework uses a new PDE-based
formulation that accounts for important and complex systems in soft
matter. These complex systems include optimal shape design in
metamaterials and fusion and fission of amphiphilic bilayer membranes.
The simulations will be performed with computational tools designed to
solve the governing PDEs both efficiently and with high-order accuracy.
The models describing granular systems could be transformative in
biomedicine and material science. The research draws from expertise in
scientific computing, physics of fluids, and mathematics. The
mathematical component incorporates variational techniques and offers
insight into fundamentals of self-organization and collective dynamics.
The project brings socially consequential research into the classroom
and offers undergraduates the opportunity to train alongside faculty and
graduate students. With its combination of mathematical modeling,
analysis, and scientific computing, the project highlights the potential
advancement of STEM from Applied Mathematics.
